%! Author = Admin
%! Date = 02.03.2026


\section*{Список литературы}

\begin{enumerate}

    \item Jiaqi Shi, Suiping Zhou, Xinwen Man, Chenyang Li, Feng Guo. Trajectory planning and tracking for UAVs with deep reinforcement learning and adaptive nonlinear MPC //
    Expert Systems with Applications. — 2025.
%    [Электронный ресурс]. —
%    URL: https://www.sciencedirect.com/science/article/pii/S0957417425042642
%    (дата обращения: 12.12.2025).

    \item Sarah P. Madruga, Augusto H. B. M. Tavares, Saulo O. D. Luiz, Tiago P. do Nascimento, Antonio Marcus N. Lima. Aerodynamic Effects Compensation on Multi-Rotor UAVs Based on a Neural Network Control Allocation Approach //
    IEEE/CAA Journal of Automatica Sinica. — 2021.
%    [Электронный ресурс]. —
%    URL: https://www.ieee-jas.net/en/article/doi/10.1109/JAS.2021.1004266
%    (дата обращения: 12.12.2025).

    \item Li-Fan Wu, Zihan Wang, Mo Rastgaar, Nina Mahmoudian. Neural Network-PSO-based Velocity Control Algorithm for Landing UAVs on a Boat //
    arXiv. — 2023.
%    [Электронный ресурс]. —
%    URL: https://arxiv.org/pdf/2309.13679
%    (дата обращения: 12.12.2025).

    \item Wenna Wang, Huaming Qian. A hierarchical ORCA framework for Multi-UAV navigation in unstructured environments with velocity optimization and local minima avoidance //
    Expert Systems with Applications. — 2025.
%    [Электронный ресурс]. —
%    URL: https://www.sciencedirect.com/science/article/pii/S0957417425028210
%    (дата обращения: 12.12.2025).

    \item Akshya J, Neelamegam G, C. Sureshkumar, Nithya V, Seifedine Kadry. Enhancing UAV Path Planning Efficiency through Adam-Optimized Deep Neural Networks for Area Coverage Missions //
    Procedia Computer Science. — 2024.
%    [Электронный ресурс]. —
%    URL: https://www.sciencedirect.com/science/article/pii/S1877050924006707
%    (дата обращения: 12.12.2025).

    \item Cezary Kownacki, Slawomir Romaniuk, Marcin Derlatka. Applying neural networks as direct controllers in position and trajectory tracking algorithms for holonomic UAVs //
    Sensors. — 2024.
%    [Электронный ресурс]. —
%    URL: https://pmc.ncbi.nlm.nih.gov/articles/PMC11993649/
%    (дата обращения: 12.12.2025).
    \item Мирошник И. В., Никифоров В. О., Фрадков А. Л. Нелинейное и адаптивное управление сложными динамическими системами. — 2000.
    \item Борисов О. И., Каканов М. А., Живицкий А. Ю., Пыркин А. А. Робастное траекторное управление квадрокоптером по выходу на основе геометрического подхода // Известия высших учебных заведений. Приборостроение. — 2021. — Т. 64, № 12. — С. 982—992.
    \item Ким С. А., Пыркин А. А., Борисов О. И. Алгоритмы управления движением квадрокоптера в режиме динамического позиционирования // Известия высших учебных заведений. Приборостроение. — 2023. — Т. 66, № 10. — С. 834—844.
    \item Ким С. А., Пыркин А. А., Борисов О. И. Алгоритмы согласованного траекторного управления движением квадрокоптера // Известия высших учебных заведений. Приборостроение. — 2024. — Т. 67, № 5. — С. 385—394.


\end{enumerate}